---
title: "P8105 Homework 6 Solutions"
author: Meghan Bellerose
date: November 21, 2020
output:
    html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

# Problem 1

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1,
    )
  ) %>% 
  filter(city_state != "Tulsa, AL",
         victim_race %in% c("White", "Black")) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
model_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, 
          ~glm(resolution ~ victim_age + victim_race + victim_sex,
            data = .x,
            family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
   select(city_state, term, OR, starts_with("CI"))
```

```{r}
model_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.6))
```

This plot shows the adjusted odds ratios and confidence intervals for solving homicides comparing Black victims to white victims in different US cities. We can see that in New York City and Baton Route, the odds of solving a homicide involving a Black American is lower than the odds of solving it for a White American.

# Problem 2

This problem uses data on children's birth weights. In the following code chunks, I show the process I used to come up with a linear regression model with the outcome birth weight `btw`. 

#### Fitting a model

**1. Load and clean the dataset for regression analysis** 

```{r}
birthweight_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    mrace = as.character(mrace), 
    mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other"),
    mrace = fct_infreq(mrace),
    babysex = as.character(babysex),
    babysex = recode(babysex, "1" = "Male", "2" = "Female"),
    babysex = fct_infreq(babysex),
    frace = as.character(frace), 
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "9" = "Unknown"),
    frace = fct_infreq(frace),
    malform = as.character(malform),
    malform = recode(malform, "0" = "Absent", "1" = "Present"),
    malform = fct_infreq(malform)
    )
  
```

**2. Look at the data**

I'll first explore three predictors that have been found to be associated with birth weight in published analyses. 

Birth weight by mother's age at delivery

```{r}
birthweight_df %>% 
  ggplot(aes(x = momage, y = bwt, color = mrace)) +
  geom_point() +
   labs(
    title = "Baby birthweight by mom age and race",
    x = "Mother's age",
    y = "Birth weight (g)",
    legend = "race")
```

Birthweight by average number of cigarettes smoked per day during pregnancy

```{r}
birthweight_df %>% 
  ggplot(aes(x = smoken, y = bwt, color = mrace)) +
  geom_point() +
   labs(
    title = "Baby birthweight by smoking status and race",
    x = "Average cigarettes smoked per day during pregnancy",
    y = "Birth weight (g)",
    legend = "race")
```

**3. Fit data**

Based on these plots, it looks like race and mom's age at birth may have a linear relationship with birth weight, so I will fit a linear model using both of those predictors. 

```{r}
fit = lm(bwt ~ momage + mrace, data = birthweight_df)
```

```{r}
fit %>% 
  broom::glance()
```

```{r}
fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "momage", "Mom's Age at Birth")) %>% 
  mutate(term = str_replace(term, "mrace", "Race: ")) %>% 
  knitr::kable(digits = 3)
```

**4. Add residuals**

```{r}
birthweight_df %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = mrace, y = resid)) +
  geom_violin()

birthweight_df %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = momage, y = resid)) +
  geom_point() +
  facet_wrap(. ~ mrace)
```

The residuals seem to have a fairly consistent distribution, so we will continue with the linear regression model.


```{r}
modelr::add_predictions(birthweight_df, fit)
```
**5. Make plot of modeled residuals against fitted values**

```{r}
birthweight_df %>% 
  modelr::add_residuals(fit) %>%
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_violin()
```


#### Now I will compare my model to two others

**Model 1: Length at birth and gestational age as predictors (main effects only)**

Look at the data
```{r}
birthweight_df %>% 
  ggplot(aes(x = blength, y = bwt, color = gaweeks)) +
  geom_point() +
  labs(
    title = "Birthweight by baby length and gestational age",
    x = "Length at birth (cm)",
    y = "Birth weight (g)")
```
Fit data
```{r}
fit_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
```

```{r}
fit_2 %>% 
  broom::glance()
```

```{r}
fit_2 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "blength", "Baby length at birth (cm)")) %>% 
  mutate(term = str_replace(term, "gaweeks", "Gestational age (weeks)")) %>% 
  knitr::kable(digits = 3)
```
Residuals
```{r}
birthweight_df %>% 
  modelr::add_residuals(fit_2) %>% 
  ggplot(aes(x = blength, y = resid)) +
  geom_point()

birthweight_df %>% 
  modelr::add_residuals(fit_2) %>% 
  ggplot(aes(x = gaweeks, y = resid)) +
  geom_point()
```

Predictors
```{r}
modelr::add_predictions(birthweight_df, fit_2)
```

Plot
```{r}
birthweight_df %>% 
  modelr::add_residuals(fit_2) %>%
  modelr::add_predictions(fit_2) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_violin()
```

**Model 2: Head circumference, length, sex, and all interactions between these  three**

Look at the data
```{r}
birthweight_df %>%
  group_by(babysex) %>% 
  ggplot(aes(x = bhead, y = bwt, color = blength)) +
  geom_point() +
  labs(
    title = "Birthweight by baby head circumference and length (male)",
    x = "Head circumference (cm)",
    y = "Birth weight (g)") +
  facet_grid(rows = vars(babysex))

```

Fit data
```{r}
fit_3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birthweight_df)
```

```{r}
fit_3 %>% 
  broom::glance()
```

```{r}
fit_3 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "blength", "Baby length at birth (cm)")) %>% 
  mutate(term = str_replace(term, "bhead", "Baby head circumference (cm)")) %>%
  mutate(term = str_replace(term, "babysex", "")) %>%
  knitr::kable(digits = 3)
```
Residuals
```{r}
birthweight_df %>% 
  modelr::add_residuals(fit_2) %>% 
  ggplot(aes(x = blength, y = resid)) +
  geom_point()

birthweight_df %>% 
  modelr::add_residuals(fit_2) %>% 
  ggplot(aes(x = gaweeks, y = resid)) +
  geom_point()
```
Predictors
```{r}
modelr::add_predictions(birthweight_df, fit_2)
```
Plot
```{r}
birthweight_df %>% 
  modelr::add_residuals(fit_2) %>%
  modelr::add_predictions(fit_2) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_violin()
```


**Comparison using cross validation**



# Problem 3

This problem uses 2017 Central Park weather data 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Test with one model fit first before bootstrapping
from broom tidy, pull values, multiply, and take log

